---
title: "Publishing to github pages"
author: "A Hart"
institute: "American university"
date: "08 May 2023"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: "16:9"
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
  message = F, warning = F, eval = T, echo = F,
  fig.align = 'center', dev = 'svglite'
)
```


# Prep materials

- `knit` file as normal in RStudio

- Rename `html` output to `index.html`  


---
# Create repository

- Go to your `github` profile, and then repositories -> New  

- Give plain language name  

- Set basic options:  
  - Public setting  
  - Add a README
  - Choose a license and `.gitignore` if you want


---
# Post and deploy

- Upload/push **all** project files to your repository  

- Go to Settings -> Pages. Under "Branch" change `None` to `main` and Save.

- Check the link in environments to see if it worked.


---
# an image just so you know

```{r}

  plot(mtcars$mpg, mtcars$wt)

```

